\chapter{Solving}

\input{6-solving/intro/index}

\input{6-solving/moves/index}
How intimidating it is for a newcomer to a new city.

\section{Principle of Heuristics}
\subsection{Computational Cost Saving}

\input{6-solving/analogy}

\input{6-solving/local/index}
% \section{Possible Hidden Places}
\subsection{Solve Like a Fox}
Don't try to generalize too early, and don't try to be perfect early on. The reason is simple, the cost is too much and the resource is limited. We can explore everything and make perfect choice at each step, the only way we could do is moving along. The wisdom is not even doing your best but to do the thing you can do, making progress instead of waiting for the right time or making the perfect match to your problem.

You can come up an idea and try it, then modify it later, and even you are improving it by visiting it multiple times. This strategy is simple but maybe powerful. It released the tension of limited resources. And it guesses along or maybe even believe its own ability that the result is at the reach and improve its understanding (I should define this word more precisely) along the way.

Solving a problem with ad hoc techniques may give the first hint of generalizations. But this route might be easier using the brutal force method rather the abst ract way thinking. We'd better revist the problem after solving, which will be a separate topic in the future.

The way of heuristics works in this book is that: in the indistinguishable path choosing situation, by assuming something may work,

\subsection{Increase the Similiarity}

\begin{example}
  If $2a+2^a = 5, 2b+ 2\log_2{(b-1)} = 5$, what is $a+b$?
\end{example}

You can solve $a$, which is around $1.28315$, and you can also get $b$, approximately $2.21685$. And the addition of these two numbers is exactly $3.5$. The important part of the transformation is to change the first part to $2a + 2 \cdot 2^{a-1} = 5$, so the two expression can have a symmetric look.

\input{6-solving/tool/index}

\section{Variable-Based Strategies}
\subsection{Completeness of Information}

\section{Trial-Based Induction}

\section{Multi-Layer Exploration}

\section{The Generic Solving Algorithm}
\subsection{Frequecy of Usage}
\subsection{Comfort of Familiarness}
\subsection{Toolbox Hierarchy}
Analogy of a memory hierarchy.
\subsection{Automatic Exploration}

\section{Reviewing the Solution}
\subsection{Hardness of a Problem}
\subsection{Evaluation of the Solution}
\subsection{Improvements of the Solution}
\subsection{Improvements of the Solving Ability}

% Real World Problems
% Not sure should I include these.
\input{6-solving/smart/index}

% \section{Real-Life Solving}
% \subsection{Hierarchy of Human Needs}
% \subsection{Complexity of Human Aesthetic}
% \subsection{Sensibility of Human Aesthetic}
% \subsection{Alternative Reality}

\section{Designing the Solver}
\subsection{Benefits of the Solver}
\subsection{Revolution on the Foundation of Mathematics}
\subsection{Universal Algorithm of Distinguishability}
\subsection{Reinvent the Wheel}
\subsection{The End of Road}

The only problem we need to solve to solve all problems is the problem of problem solving.

So, why not solve it?
