\section{Training the Human Learners}

From vague, inconfident, chaotic, erroneous, strange to clear, confident, accurate, fluent, familiar.

\subsection{Conceptual Leaps}
\subsection{Training the Robust Techniques}
Most of the time, the resaon you solve a problem that you consider it as hard is because you have practiced it very hard.

Practise gives you lots of pleasure and also a data to induct a rule from.

\subsection{The Necessity of Repetition}
The retention is the mother of repetition. And people have conflict feelings about training the robust techniques. At one hand, people encourage people to practice, especially delibrate practice. On the other hand, you find people think creativity trumphs recipe type procedure.


\subsection{Training the Generic Techniques}

It seems like the education institution wants to teach pupils about real thinkings instead of rote memorization. And the reality is that it's just the generic techniques with weak robustness, the teachability seems low, since there are differences between human individuals, some learners can perform way better than the others.

\subsection{Learnability for Human Learners}
If the students are capable to do something without the help of the teachers, the Necessity of education is self-learning for the students for the rightful accessability for this learner. But for the other students what they need is a way of learning with proper level of accessability not others.

\subsection{Accessability of Training Tools}

Even with the worst training tool, the brightest kid can learn fast.

The learning materials like roads that some are smooth and some are murdy, and the learner is like the car with different engines and tires. Some are very powerful and some are not.

The progress of human education is essential a way to smooth the road. That once bumpy sand road change to cement one. One great example in the multiplication of roman numbers, Roman has the right of pride, but its number is truly not efficient to calculate. The arrival of the Arabic number, along side the invention of logrithm, makes normal people able to learn more, to break the barrier once unnecessarily thick and trainned more and be able to make more and contribute more to the progress of the human society.

Even in our ages, I don't understand lots of the training neccessaty for the time wasting competitive purpose. That we have to curve students so some of them have the right of the limited resources. The misleading part of this is that lots of people can't even be trainned sufficient to their intelligence.

We are always amazed how human can beat computers, but only in a category of stuffs. And we are also troubled by educating the real intelligence. That means sometimes you can't explain with programming, you can't explain to people.

So I found this interesting is that the teachability and computability. People are good at pattern recognization, which as discussed earlier is the result of the ability to find distinctions and determine the degree of distinction.

What is the differency

\subsection{Limitations of Training}

The robustness of a technique, and the solving radius of it, should be a center topic of education and solving algorithms.

Normally, as I personally experienced, that more robust a technique appears, the solving radius is smaller. Or maybe because we consider it as small not essentially small. Once you invented a new technique, people could use it to solve problems, but also they could find the situations where the technique is not suitable, you need a new trick or most of the time, a higher level of strategy with bigger solving radius, but this is vague. That means you have to master a skill that you only practice once, or you have to paint a picture by seeing it for a few seconds, the signal are so weak, the possible directions are so many, you couldn't choose where to go and you can't give a suitable instance to satisfy your need.

Here we can give you a solid example in solid geometry:

How to find the dihedral angle of given two plains. The technique to solve is straightforward, you just find two surface normals, and the angle of these two is nearly the answer.

But what tricky is how can you find the two surface


You can't train too much abstract techniques, especially generic ones. But there are difference of intelligence among learners which set us apart.
