\subsection{Purposely versus Mechanically}

The mechanics of mechanical moves works like this: see A, tranform it to B. We despise the mechanical and prise the artistic actions. Even the once brilliant solution, as used by many will become a cliche someday, though we appreciate its robustness, but not its ingenuity.

While moving purposely involves intelligence at least to us, and this argument is vague. If the signal is strong and the transformation after it is easy to follow, we may consider it as mechanical. But if the signal is weak and we can't define it and easy to recognize it, we can't even trust this argument too much. Since the inconsistency and ambiguity is all around the purposely movements.

Let's define something here, that if it's easily imitated, it's weak in intelligence. So the only thing we agree on is that complexity is hard to imitate, so by being intelligent it means you are complexty to explain, but can be explained.

Here is the thing searching is the true complicated computing procedure. And recognizing is hard too. And when we say craft, we mean the numerous hands-on experiences, and through these experiences, we can store large amount of information to induce its pattern from. And also the brain can have more time to process more details and maybe rescan the data again and again to improve the understanding of the pattern and the inner structure or the optimized point of the procedure. So machine learning somehow works pretty well on these tasks that you can understand the naunce pattern some data may possess.
