\section{Smartness of a Human Solver}
\subsection{Illusion of Competence and Incompetence}

When you read a popular book and watch a tutorial on YouTube, you seem like you understand the concepts quickly, and the subjects are easy and you can also remake it easily. But you are wrong for sometimes.

First, you can't reproduce the procedure reliablely, you just follow each step, rather walking the path yourself. When you solve the problem independently, you will find there are many crossroads and not sure which direction to go.

Second, you are able to understang the local procedure and remember it, but soon your memory will evapor and you have to recall and repeatly read or play.

Third, to invent is to choose, not to follow. There are so many combinations to work something out, but few are working and easy to communite. The masterpiece requires many choices normal people can't decide.

But sometimes you feel stupid when you study some subjects. But it's because the materials aren't good enough.

First, it might be too abstract too early on. Too few examples make you feel overwhelming and you can't use your feature extraction ability the evolution have provide. You are not a computer, you are more capable to do things current computer can't do, that's to find the pattern through data, find links between objects.

Second, if you can understand what a teacher teachs, but can't workout the similiar problems in the exercise, most of the time is that the teacher teaches you a problem that's easy to follow, but hard to solve, cause the teacher have the illusion of competence and he or she has the opportunity to read solutions and explain it to you, and he or she has more experience to choose from and maybe has more advanced strategies he or she might not even noticing using and can't teach you that. But the blame is on you, cause you can't solve the problem.

\subsection{Basic Requirements for Being Intelligent}

You have to be smart to understand the meaning of smartness. It's hard to distinguish from lucky and smart.

The ability of abstraction is in subconscious, and that is hard to touch and understand. And I guess this is also untrainable somehow. Subconscious is a blackbox, you can't really know too much about it.

\subsection{Mysterious Human Aesthetic}
\subsection{Sensibility of Human Aesthetic}
\subsection{Imagining the Alternative Reality}
\subsection{Solvability for Human Solvers}

You have to be healthy and relaxed to solve hard problems.
