\section{Distinguishability}

Cue is what you can distinguish from environments but also indistinguishable from time to time.

\subsection{100 Examples of Distinguishability}

This is a personal $\computation$ project to give as much as real life example possible. Since I can experience reunderstand the world again and again. So I have to write them down as a way to show the importancy of this fundamental concepts.

To realize the importancy of distinguishability is the biggest revelation in my life.

1. Human brain should have several similiar areas of distinguish data.

2. Those areas are the same.

3. To distinguish is the most important functionality of the brain.

4. distinguish with a degree works great both for discrete objects and for the class level objects.

Your brains are capable to distinguish for tolerance level of clarity.

When it is easy to distinguish then no detail distinction is needed. If things are get strict, deeper inspect should be considered.

When we extrapolate, what we're based on is that we can't distinguish things for all object in that class under those circumstances.

% \subsection{Information}

Everything we do everyday is basic four actions: distinguish things, recognize things, transform things and associate things.

Distinguishability permeates every aspects of intellectual pursuit.

\textbf{Cue} is what you can distinguish from environments but also indistinguishable from time to time.

I believe what makes us so superior is because we could quickly find out something distinguishable in a degree.

Most of the time we only care it's distinguished or not.

Information means distinguished objects after distinction. But distinguishability means the level beneath information.

The foundation of information lies on distinguishability. How contrast and how unique an object is.
% \subsection{Ambiguity and Inconsistency}
\input{1-computation/distinguish/examples}
\input{1-computation/distinguish/indistinguish}
